### 2012-09-05 intention motor representation joint action (paper 3)/conf collective intentionality manchester 2012/motor representation and shared intention.tex
tidying up after various talks

This gives rise to a challenge. 
Effective joint action—imagine two people erecting a tent in a gale together—sometimes requires both shared intentions and social motor representation plus a certain kind of harmony between the two. 
To characterise the harmony required, let us define a notion of matching:
%
\begin{quote}
Two  outcomes, A and B, \emph{match} in a particular context just if, in that context, either the occurrence of A would normally constitute or cause, at least partially, the occurrence of B or vice versa. 
\end{quote}
%
When joint action involves both shared intention and social motor representation, the outcomes each of these representations specify should match.
This is the required harmony.
The challenge is to explain how matching could ever non-accidentally occur.
%This will be particularly difficult if you suppose, as we do, that motor representation and intention are not inferentially integrated.

I think we can see a possible solution to this challenge by considering another problem.
In building shared intention from ordinary individual intention, we need intentions \emph{that we J}.
As has been much discussed, the contents of these intentions cannot all refer to actions involving shared intentions.
For this reason Michael Bratman suggests that things we intend are  cooperatively neutral activities.
It is then necessary to add further intentions in order to transform cooperatively neutral activities into joint actions.
But it also seems possible that in some cases, what we intend when we intend that we J is not a cooperatively neutral activity but instead a joint action of the sort which involves social motor representation.

@@

>>>>

This gives rise to a challenge. 
Effective joint action—imagine two people erecting a tent in a gale together—sometimes requires both shared intentions and social motor representation plus a certain kind of harmony between the two. 
To characterise the harmony required, let us define a notion of matching:
%
\begin{quote}
Two  outcomes, A and B, \emph{match} in a particular context just if, in that context, either the occurrence of A would normally cause or constitute, at least partially, the occurrence of B or vice versa. 
\end{quote}
%
When joint action involves both shared intention and social motor representation, the outcomes each of these representations specify should match.
This is the required harmony.
The challenge is to explain how matching could ever non-accidentally occur.
%This will be particularly difficult if you suppose, as we do, that motor representation and intention are not inferentially integrated.

I think we can see a possible solution to this challenge by considering another problem.
In constructing realisers of shared intention from ordinary individual intention, we need intentions \emph{that we J}.
As has been much discussed, the contents of these intentions cannot all refer to actions involving shared intentions.
For this reason Michael Bratman suggests that things we intend are  cooperatively neutral activities.
It is then necessary to add further intentions in order to transform cooperatively neutral activities into joint actions.
But it also seems possible that in some cases, what we intend when we intend that we J is not a cooperatively neutral activity but instead a joint action of the sort which involves social motor representation.

@@

In conclusion, two things.
First, some events are joint actions in virtue of being appropriately related to social motor representations which bind their components together and ensure that there is a single outcome to which these components are collectively directed.
Second, and much more tentatively, in some cases social motor representation may be among the ingredients that realise a shared intention.
